Towards Detecting Stalkerware Through Network Traces

### 2019-03-19 paper/main.tex
edit traffic result

\usepackage{makecell}
\renewcommand\cellalign{tl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

PUT NOTE HERE ABOUT THE FAMILIES THAT WE DID NOT CONFIRM VIA TRAFFIC, BUT 
INSTEAD VIA LOOKING AT THE WEBSITES!! Otherwise we're fabricating results.

>>>>

\usepackage{makecell}
\usepackage{booktabs}
\renewcommand\cellalign{tl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

Apps be identify as reskinned by observing their websites. We found several groups with similar dashboards (where users view the communications and locations of the target phones), download sites, and advertisements. Several groups of off-store apps have nearly identical websites, in terms of organization, color, fonts, placement of buttons, prices, and other factors. For example, the “ILFMobile group” consists of three different companies (ILFMobile, PowerLine Group, and PhoneSpector) that claim to make a total of four different apps. Further investigation showed that all three companies had the same physical address in addition to identical websites. Unfortunately, they also had identical bugs in their payment methods, so we were unable to purchase the apps and verify that their network traces were identical.
